S-Tipping vs B-Tipping

### 2018-05-18 paper/paper.Rmd

---
title: S-Tipping vs B-Tipping
## We can figure out author order later on who end up doing more etc :-)
author:
  - name: Ryan Batt
    affiliation: epa
  - name: Carl Boettiger
    email: cboettig@berkeley.edu
    affiliation: espm
    footnote: Corresponding Author

address:
  - code: espm
    address: Department of Environmental Science, Policy, and Management, University of California, Berkeley, CA 94720
  - code: epa
    address: Environmental Protection Agency, ...
abstract: |
  This is the abstract.

>>>>

---
title: S-Tipping vs B-Tipping
## We can figure out author order later on who end up doing more etc :-)
author:
  - name: Ryan Batt
    affiliation: rpirutgers
  - name: Carl Boettiger
    email: cboettig@berkeley.edu
    affiliation: espm
    footnote: Corresponding Author

address:
  - code: espm
    address: Department of Environmental Science, Policy, and Management, University of California, Berkeley, CA 94720
  - code: rpirutgers
    address: Rensselaer Polytechnic Institute and Rutgers University
abstract: |
  This is the abstract.
